### 2022-05-06 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@a246124feaeeda2ef7c9aff0b272e1e5264cc10b 🚀

\vfill
Driven by the need to understand the ecological factors involved in the
emergence of betacoronavirus through bat hosts, we develop an approach
to the assesment of spillover risk based on the Geographic Mosaic Theory
of Coevolution. In doing so, we provide a global mapping of the risk
posed by viruses, reflecting the fact that this risk has many ecological
and evolutionary origins. Our framework reveals that reservoir richness
alone is not a sufficient predictor of risk, and offers alternative
insights based on viral sharing, host compositional uniqueness, and host
phylogenetic diversity. By comparing our aggregated measure of risk to a
proxy for human density, namely the proportion of each pixel that is
covered by urban or built land, we provide a synthetic risk map,
allowing the identification of hotspots where the bat-betacoronavirus
system may originate novel viruses in humans.

>>>>

\vfill
Driven by the need to understand the ecological factors involved in the
emergence of betacoronavirus (the genus causing the SARS and MERS
disease in human) through bat hosts, we develop an approach to the
assesment of spillover risk based on the Geographic Mosaic Theory of
Coevolution. In doing so, we provide a global mapping of the spillover
risk posed by betacoronaviruses, reflecting the fact that this risk has
many ecological and evolutionary origins. Our framework reveals that
reservoir richness alone, although a component of viral hazard, is not a
sufficiently integrative predictor of risk. We offer alternative
insights based on viral sharing, host compositional uniqueness, and host
phylogenetic diversity. By comparing our aggregated measure of risk to a
proxy for human density, namely the proportion of each pixel that is
covered by urban or built land, we provide a synthetic risk map,
allowing the identification of hotspots where the bat-betacoronavirus
system may originate novel viruses in humans.

### 2022-05-06 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@a246124feaeeda2ef7c9aff0b272e1e5264cc10b 🚀

Driven by the need to understand the ecological factors involved in the
emergence of betacoronavirus through bat hosts, we develop an approach
to the assesment of spillover risk based on the Geographic Mosaic Theory
of Coevolution. In doing so, we provide a global mapping of the risk
posed by viruses, reflecting the fact that this risk has many ecological
and evolutionary origins. Our framework reveals that reservoir richness
alone is not a sufficient predictor of risk, and offers alternative
insights based on viral sharing, host compositional uniqueness, and host
phylogenetic diversity. By comparing our aggregated measure of risk to a
proxy for human density, namely the proportion of each pixel that is
covered by urban or built land, we provide a synthetic risk map,
allowing the identification of hotspots where the bat-betacoronavirus
system may originate novel viruses in humans.

>>>>

Driven by the need to understand the ecological factors involved in the
emergence of betacoronavirus (the genus causing the SARS and MERS
disease in human) through bat hosts, we develop an approach to the
assesment of spillover risk based on the Geographic Mosaic Theory of
Coevolution. In doing so, we provide a global mapping of the spillover
risk posed by betacoronaviruses, reflecting the fact that this risk has
many ecological and evolutionary origins. Our framework reveals that
reservoir richness alone, although a component of viral hazard, is not a
sufficiently integrative predictor of risk. We offer alternative
insights based on viral sharing, host compositional uniqueness, and host
phylogenetic diversity. By comparing our aggregated measure of risk to a
proxy for human density, namely the proportion of each pixel that is
covered by urban or built land, we provide a synthetic risk map,
allowing the identification of hotspots where the bat-betacoronavirus
system may originate novel viruses in humans.
